Estimating the Initial Susceptible Fraction in Dengue Dynamics

### 2015-02-01 draft_lm1.tex
moved the paragraph discussing uncertaities to discusion. Closes #14

It is also important to consider other sources of uncertainty impinging on the 
estimation of the AR of a dengue epidemic. 
For instance, in any given epidemic there is a large number of 
mild and asymptomatic cases, which nevertheless acquire immunity.
Depending on surveillance structure it is estimated that for every case 
reported, up to 10-20 are not seen by health authorities (personal 
communication).
%LM: Best to name who gave that. Oswaldo perhaps?
Another source of uncertainty is under-reporting, which is a serious issue in
the health care systems of many underdeveloped countries such as Brazil. 
Duarte and Fran\c{c}a (2006)~\cite{duarte_data_2006}, estimated 
the sensitivity of dengue reporting for hospitalized patients in 
Belo-Horizonte, Brazil to be of 63\%, meaning that approximately 37\% of the 
suspected dengue cases go unreported.  
Lastly, demography and migrations affect the number of susceptible in ways 
which 
are not easy to fully determine.
%LM: Since this paragraph pretty much deals with possible limitations we may 
% want to move it to the discussion. see #14

@@

>>>>

@@

We sought to deal with all important sources of uncertainty impinging on the 
estimation of the AR of a dengue epidemic, but not all could be satisfactorily 
addressed in this analysis.
For instance, in any given epidemic there is a large number of 
mild and asymptomatic cases, which nevertheless acquire immunity.
It is estimated that for every case reported, up to 10-20 are not seen by health 
authorities (Oswaldo G. Cruz, personal communication).

Another source of uncertainty is under-reporting, which is a serious issue in
the health care systems of many developing countries such as Brazil. 
Duarte and Fran\c{c}a (2006)~\cite{duarte_data_2006}, estimated 
the sensitivity of Dengue reporting for hospitalized patients in 
Belo-Horizonte, Brazil to be of 63\%, meaning that approximately 37\% of the 
suspected Dengue cases go unreported.  
Lastly, demography and migrations affect the number of susceptible in ways 
which are not easy to fully determine.
